---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# National Eutrophication Survey Data Package

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/nesRdata)](https://cran.r-project.org/package=nesRdata)

## Installation

```{r installation, eval=FALSE}
# install stable version from CRAN
install.packages("nesRdata")

# install development version from Github
# install devtools if not found - install.packages("devtools")
# devtools::install_github("jsta/nesRdata", update_dependencies = TRUE)
```


## Usage

```{r load_package}
library(nesRdata)
```

### View static compilation of all lakes

```{r static}
data(nes)
head(nes)
```

### Download dynamic external data to temporary location

```{r get_temp, message=FALSE, eval=FALSE}
nes_get(version_id = "5")
```

### Download dynamic external data and cache in file system

```{r get_cached, message=FALSE, eval=FALSE}
nes_get(version_id = "5", dest_folder = cache_path())
```

#### List cached (non-temporary) versions

```{r versions, eval=FALSE}
nes_versions()
```

#### Load data

```{r load_data, eval=FALSE}
dt <- nes_load(version_id = "5")
names(dt)
lapply(dt, head)
```

## Metadata

`help.search("^nes$", package = "nesRdata")`

## References

Stachelek, J., Ford, C., Kincaid, D., King, K., Miller, H. and Nagelkirk, R., 2018. The National Eutrophication Survey: lake characteristics and historical nutrient concentrations. Earth System Science Data, 10(1), pp.81-86.
